---
title: "Lab 00 - Hello IDS!"
author: "Nadav L"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Mgraff", "Adian something", "Libby", 
           "Ella", "Maya"),
  github_username = c("mcgregors-garden", "aidancrocket06", "pmcrath735", 
                      "libby-ald", "maya2468"), 
  colour = c("blue", "blue", "purple", 
             "green", "red"),
  hobby = c("fishing", "cooking", "woodworking", 
            "skydiving", "miniture figure painting"),
  favourite_number = c(2, 5, 5, 5, 5)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


A bar graph of peoples github usernames against theyre favourite colour

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "username", 
          y = "favourite number",
          title = "peoples fvourite number")
```

labs() -> labels the plot, given axis and a title

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

As the number of possible hobbies greatly outnumbers the amount of people sampled, a bar graph is not suitable,
they are more suited in cases when a large variance of values between a couple of options
perhaps a more suitable graph would be a word cloud.
